---
title: "Beatriz Milz's resume"
author: Beatriz Milz
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
    css: ["css/resume.css"]
    
# to render into pdf: pagedown::chrome_print("docs/index.html")
# If needed:
# https://pagedown.rbind.io/
# https://www.pagedmedia.org/about-paged-media/pagedjs-cheatsheet/
# https://slides.yihui.name/2019-rstudio-conf-pagedown.html#1
# xaringan::inf_mr("docs/index.Rmd")
---
Aside
================================================================================



Summary {#summary}
--------------------------------------------------------------------------------

<i class="fas fa-graduation-cap"></i> Doctoral Student in Environmental Science at University of Sao Paulo (USP).

<i class="fab fa-r-project"></i> R enthusiast. 

<i class="fab fa-meetup"></i> R-Ladies Sao Paulo Co-organizer. 



Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> beatriz.milz@usp.br

- <i class="fa fa-phone"></i> (+55) 11 98420-2780

- <i class="fa fa-github"></i> [Github: beatrizmilz](https://github.com/beatrizmilz)

- <i class="fa fa-external-link-alt"></i> [Lattes CNPQ](http://lattes.cnpq.br/5150665880581477) 

- <i class="fa fa-linkedin"></i> [Linkedin](https://br.linkedin.com/in/beatrizmilz) 


- <i class="fa fa-home"></i> https://beatrizmilz.com

- For more information, please contact me via email.


Languages {#languages}
--------------------------------------------------------------------------------
**Portuguese:** Native

**English:** Proficient

**Spanish:** Beginner


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

This resume is **not** complete.

Code available on <i class="fa fa-github"></i>  [Github](https://github.com/beatrizmilz/resume). 

Last updated on `r Sys.Date()`. The most recent version of this resume is [available here](https://beatrizmilz.github.io/resume/index.pdf). 





Main
================================================================================

Beatriz Milz {#title}
--------------------------------------------------------------------------------

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### University of São Paulo

**Doctoral Student in Environmental Science**       <br> Institute of Energy and Environment <br> Graduate Program in Environmental Science

São Paulo, SP, Brazil

2019 - Currently

**Research project:** [Active Transpacency in the water resources management in Sao Paulo Macrometropolis using the INTRAG method](https://bv.fapesp.br/en/bolsas/185176/active-transparency-in-the-management-of-water-resources-in-the-sao-paulo-macrometropolis-using-the/)

**Scholarship:** FAPESP  Grant number: 18/23771-6


**Advisor:** [Pedro Roberto Jacobi]( http://lattes.cnpq.br/6799067928413168) 

### Federal University of São Paulo

**M.S. in Sciences** <br> Institute of Environmental, Chemical and Pharmaceutical Sciences <br> Graduate Program in Integrated Environmental Analysis

N/A

2016 - 2018

**Dissertation:** Evaluation of the water quality and remote sensing mapping (LANDSAT-8/OLI) of the Central Body I of the Billings Reservoir (São Paulo, SP)

**Advisor:** [Cristina Souza Freire Nordi](http://lattes.cnpq.br/1133827212627122) 

### University of São Paulo

**Bachelor degree in Environmental Management**       <br> School of Arts, Sciences and Humanities 

N/A

2012 - 2015

**Undergraduate thesis:** Use of the Billings reservoir for public supply in the Metropolitan Region of Sao Paulo in the context of water crisis: The interligation of the Billings reservoir and the Alto Tietê System.

**Advisor:** [Pedro Roberto Jacobi]( http://lattes.cnpq.br/6799067928413168) 

Research Projects {data-icon=laptop}
--------------------------------------------------------------------------------

### MacroAmb FAPESP

FAPESP Thematic Project - [Environmental Governance of the Sao Paulo Macrometropolis in face of climate variability](https://bv.fapesp.br/en/auxilios/97000/environmental-governance-of-macrometropolis-paulista-in-face-of-climate-variability/) - Grant number: 15/03804-9

N/A


2018 - Currently  


Projects {data-icon=share-alt}
--------------------------------------------------------------------------------
### [R-Ladies Sao Paulo Co-organizer](https://www.meetup.com/pt-BR/rladies-sao-paulo/)

https://rladies.org/

N/A

2018 - Currently


Scientific Journals - Editorial Board {data-icon=book .break-after-me}
--------------------------------------------------------------------------------

### Editorial Secretary - [Journal Ambiente & Sociedade](http://scielo.br/asoc)

N/A

N/A

2018 - Currently



Experience {data-icon=briefcase}
--------------------------------------------------------------------------------
### Federal University of São Paulo

**Teaching Internship** - Water Ecosystems <br> Institute of Environmental, Chemical and Pharmaceutical Sciences <br> Undergraduate Program in Environmental Sciences

Diadema, SP, Brazil

2017 - 2017


### City Hall of Sao Paulo

**Intern in Environmental Managment** 

São Paulo, SP, Brazil

2014 - 2015

Grants {data-icon=award}
--------------------------------------------------------------------------------

### [LatinR 2019](https://latin-r.com/) - Latinamerican Conference About the Use of R in R&D

Diversity Scholarship - Travel and Conference

Santiago, Chile

2019


### [useR! 2019](https://user2019.r-project.org/)

Diversity Scholarship - Travel and Conference

Toulouse, France

2019

### [São Paulo Research Foundation (FAPESP)](https://bv.fapesp.br/en/bolsas/185176/active-transparency-in-the-management-of-water-resources-in-the-sao-paulo-macrometropolis-using-the/)

May/2019 - Jan/2022 - Scholarships in Brazil - Doctorate - Grant number: 18/23771-6

São Paulo, SP, Brazil

2019 - 2022

Events organized {data-icon=calendar-check}
--------------------------------------------------------------------------------
### I Fórum de Governança Ambiental da Macrometrópole Paulista.

Organizing Committee

São Paulo, SP, Brazil

2019


### 2º Simpósio em Análise Ambiental Integrada

Organizing Committee

Diadema, SP, Brazil

2017

### 1º Simpósio em Análise Ambiental Integrada

Organizing Committee

Diadema, SP, Brazil

2016


Publications {data-icon=book-open} 
--------------------------------------------------------------------------------
### Anais do Seminário Internacional de Estatística com R

MILZ, B.; GONÇALVES PINTO, B. G.; WUNDERVALD, B.; SVAB, H. [Ensino de R através da comunidade R-Ladies - Capítulo São Paulo.](http://periodicos.uff.br/anaisdoser/article/view/29327)

N/A

2019



```{r eval=FALSE, include=FALSE}
ADICIONAR:
- Dialogos socioambientais
- Capítulo livro paranapiacaba (nao lançado)
- Capítulo livro adaptação (lançado!)
- Anais serve? Anais do FORUM MACROAMB, e evento USP 2016
```




Oral Communications {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------
### [useR! 2019](https://user2019.r-project.org/) - [Youtube Video](https://youtu.be/2HK6hjwhdRk?t=880)

MILZ, B.; WUNDERVALD, B. [The evolution and importance of the R-Ladies São Paulo chapter in Brazil.](https://beatrizmilz.github.io/useR2019/)

Toulouse, France

2019


### I Fórum de Governança Ambiental da Macrometrópole Paulista.

MILZ, B.; JACOBI, P. R. Levantamento exploratório de estudos sobre a Governança Ambiental na Macrometrópole Paulista. 

São Paulo, SP, Brazil

2019


###  II Simpósio Interdisciplinar de Ciência Ambiental

MILZ, B.; MACEDO, B. N. M. ; JACOBI, P. R. Transparência na gestão de recursos hídricos e a interligação dos Sistemas Rio Grande e Alto Tietê.

São Paulo, SP, Brazil

2016 


Poster Presentations {data-icon=calendar-check}
--------------------------------------------------------------------------------

### IV SER UFF - International Seminar on Statistics with R

MILZ, B.; GONÇALVES PINTO, B. G.; WUNDERVALD, B.; SVAB, H. [Ensino de R através da comunidade R-Ladies - Capítulo São Paulo.](https://beatrizmilz.github.io/resume/certificates/2019/Certificado-SER-Poster.pdf)

Rio de Janeiro, RJ, Brazil

2019


### XVI Congresso Brasileiro de Limnologia 

MILZ, B.; RIBEIRO, M. S. F. ; BITENCOURT, A. L. V. ; FREIRE-NORDI, C. S. Avaliação da qualidade da água do Corpo Central da represa Billings (São Paulo, SP) e mapeamento por sensoriamento remoto (Landsat-8/OLI).

Rio de Janeiro, RJ, Brazil

2017




### 2º Simpósio em Análise Ambiental Integrada

MILZ, B.; BITENCOURT, A. L. V. ; FREIRE-NORDI, C. S. Avaliação da qualidade da água e mapeamento por sensoriamento remoto (LANDSAT-8/OLI) do compartimento ambiental corpo central I da represa Billings (São Paulo, SP).

Diadema, SP, Brazil

2017



### 1º Simpósio em Análise Ambiental Integrada

MILZ, B.; FREIRE-NORDI, C. S. ; BITENCOURT, A. L. V. Avaliação da qualidade das águas superficiais do compartimento Corpo Central 1 da represa Billings, através do estudo de variáveis físicas e químicas e do monitoramento por sensoriamento remoto orbital (Landsat 8/OLI)

Diadema, SP, Brazil

2016

Workshops taught {data-icon=chalkboard-teacher} 
--------------------------------------------------------------------------------

### `R` - [Workshop in Portuguese - Apresentações no R ⚔ com xaringan](https://beatrizmilz.github.io/aMostra-IME-2019-Xaringan/)

[14ª aMostra Estatística](https://www.ime.usp.br/~amostra/) - Institute of Mathematics and Statistics, University of São Paulo (IME/USP)

São Paulo, SP, Brazil

2019


### `R` - [Workshop in Portuguese - Communicating your results: creating presentations with R](https://beatrizmilz.github.io/IV-SER-RLadies/)

[IV SER UFF - International Seminar on Statistics with R](http://ser.uff.br/) - [Certificate](https://beatrizmilz.github.io/resume/certificates/2019/Cert_Minicurso_Beatriz Milz2.pdf)

Niterói, RJ, Brazil

2019


### `R` - Workshop in English -  Introduction to R (R-Ladies São Paulo)

2018 CODATA-RDA School of Research Data Science - ICTP-SAIFR/NCC-UNESP

São Paulo, SP, Brazil

2018


### `R` - Workshop in Portuguese -  Introduction to R

Federal University of ABC (UFABC)

São Bernardo do Campo, SP, Brazil

2018


Meetup Presentations {data-icon=meetup} 
--------------------------------------------------------------------------------

### 2019

N/A

N/A

2019

`R` - ["Primeiros passos utilizando o Git e GitHub no RStudio"](https://beatrizmilz.github.io/RLadies-Git-RStudio-2019/), in Portuguese, Meetup R-Ladies São Paulo.

`R` - ["Introdução ao pacote xaringan - Criando apresentações com R"](https://beatrizmilz.github.io/IME-27-08-2019/),  in Portuguese,  Institute of Mathematics and Statistics, University of São Paulo (IME/USP).

`R` - [“Dashboards, gráficos, mapas: Possibilidades de visualização de dados com R”](https://beatrizmilz.github.io/NerdzaoWeek/), in Portuguese, [Meetup Nerdzão - Nerdzão Week](https://nerdzao.netlify.com/).


`R` - [“R Workshop - Intermediate”](https://beatrizmilz.github.io/2019-02-R-Interm-R-LadiesSP/#), in Portuguese, Meetup R-Ladies São Paulo.

`R` - [“R Workshop - Basic”](https://maryms.github.io/2019-02-R-Basics-R-LadiesSP/), in Portuguese, Meetup R-Ladies São Paulo.


### 2018

N/A

N/A

2018

`R` - [“Communicating your results: creating presentations with R”](https://beatrizmilz.github.io/apresentacao_RLadies_xaringan/), in Portuguese, Meetup R-Ladies São Paulo.



Events attended {data-icon=calendar-check} 
--------------------------------------------------------------------------------

### [LatinR 2019](https://latin-r.com/)

Latinamerican Conference About the Use of R in R&D

Santiago, Chile

2019

### [useR! 2019](https://user2019.r-project.org/)

[Certificate](https://beatrizmilz.github.io/resume/certificates/2019/certificate_96-useR.pdf)

Toulouse, France

2019


###  [IV SER UFF - International Seminar on Statistics with R](http://ser.uff.br/)

[Certificate](https://beatrizmilz.github.io/resume/certificates/2019/ser-participacao-CertificadoBeatriz Milz.pdf)

Niterói, RJ, Brazil

2019


### I Fórum de Governança Ambiental da Macrometrópole Paulista

N/A

São Paulo, SP, Brazil

2019


```{r eval=FALSE, include=FALSE}
# procurar esse certificado! I Fórum de Governança Ambiental da Macrometrópole Paulista
```


### 3a Conferência Brasileira de Jornalismo de Dados e Métodos Digitais (CODA BR)

Open Knowledge Brasil - 18h

São Paulo, SP, Brazil

2018


### WordCamp São Paulo 2018

10h

São Paulo, SP, Brazil

2018


### Oficina de Aprendizagem Social sobre Clima

IAG - University of Sao Paulo - 6h 

São Paulo, SP, Brazil

2018


### Diálogos interdisciplinares sobre a Governança da Macrometrópole Paulista

MACROAMB/Fapesp

São Paulo, SP, Brazil

2018


### VI Encontro Internacional de Governança da Água

Grupo de Acompanhamento e Estudos de Governança Ambiental (GovAmb)

São Paulo, SP, Brazil

2017


### VII Simpósio Ecologia de Reservatórios

UNESP Botucatu

Botucatu, SP, Brazil

2017


### XVI Congresso Brasileiro de Limnologia

N/A

Rio de Janeiro, RJ, Brazil

2017



### II Simpósio em Análise Ambiental Integrada (II SINTEGRADA)

Instituto de Ciências Ambientais, Químicas e Farmacêuticas da Universidade Federal de São Paulo (UNIFESP)

Diadema, SP, Brazil

2017


### II Simpósio Interdisciplinar de Ciência Ambiental

Institute of Energy and Environment, University of São Paulo (IEE/USP)

São Paulo, SP, Brazil

2016

### I Simpósio em Análise Ambiental Integrada (I SINTEGRADA)

Instituto de Ciências Ambientais, Químicas e Farmacêuticas da Universidade Federal de São Paulo (UNIFESP)

Diadema, SP, Brazil

2016


### V Encontro Internacional de Governança da Água

Grupo de Acompanhamento e Estudos de Governança Ambiental (GovAmb)

São Paulo, SP, Brazil

2015


Short courses Attended {data-icon=book} 
--------------------------------------------------------------------------------


### 2019

N/A

N/A

2019

[IV Curso de Atualização SciELO-ScholarOne](https://beatrizmilz.github.io/resume/certificates/2019/scielo-scholarone.pdf) - Programa SciELO/FAPESP

[III Workshop para Monitoramento de Bacias Hidrográficas](https://beatrizmilz.github.io/resume/certificates/2019/fealq-workshop-bacias.pdf) - Fundação de Estudos Agrários Luiz de Queiroz (FEALQ), 40h.

`R` - [R Programming](https://beatrizmilz.github.io/resume/certificates/2019/DS-2-Coursera-5R6SZKQCCYJ4.pdf) -  Coursera/Johns Hopkins University

`R` - [The Data Scientist’s Toolbox](https://beatrizmilz.github.io/resume/certificates/2019/DS-1-Coursera-THZN7SCGDL57.pdf) -  Coursera/Johns Hopkins University

`R` - [Dashboards with R](https://beatrizmilz.github.io/resume/certificates/2019/curso-r-dashboards.pdf) - Curso-R, 18h.

`R` - [Building web applications in R using Shiny](https://beatrizmilz.github.io/resume/certificates/2019/ser_shiny.pdf) - Dean Atalli & IV Seminário Internacional de Estatística com R, 3h.

`R` -  [Web Scraping with R](https://beatrizmilz.github.io/resume/certificates/2019/curso-r-web-scraping.pdf) - Curso-R, 8h.

`R` - [Working with geospatial data in R](https://beatrizmilz.github.io/resume/certificates/2019/datacamp-working-with-geospatial-data.pdf), Datacamp.

`R` - [Introduction to the Tidyverse](https://beatrizmilz.github.io/resume/certificates/2019/datacamp-introduction-to-the-tidyverse.pdf), Datacamp.

`R` - [R Programming Track](https://beatrizmilz.github.io/resume/certificates/2019/datacamp-r-programming-track.pdf), Datacamp.

`R` - [Writing functions with R](https://beatrizmilz.github.io/resume/certificates/2019/datacamp-writing-functions-in-R.pdf), Datacamp.

`R` - [Intermediate R](https://beatrizmilz.github.io/resume/certificates/2019/datacamp-intermediate-r-practice.pdf) - Practice Course, Datacamp.


### Proposal Formulation Workshop - Small Grants Program 

The role of ecosystem services in adapting to global change for Human Wellbeing (SGP-HW). Inter-American Institute for Global Change Research (IAI)

Online

2018


### 2018

N/A

N/A

2018


`R` -  [Reporting with R Markdown Course](certificates/2018/datacamp-reporting-with-rmarkdown.pdf), Datacamp.

`R` -  [Intermediate R Course](certificates/2018/datacamp-intermediate-R.pdf), Datacamp.



`R` - [Introduction to R Programming](https://beatrizmilz.github.io/resume/certificates/2018/curso-r-introducao-ao-r.png) - Curso-R, 16h.

`Python` -  [Intro to Python for Data Science Course](https://beatrizmilz.github.io/resume/certificates/2018/datacamp-introduction-to-python.pdf), Datacamp.

`R` -  [Introduction to R Course](https://beatrizmilz.github.io/resume/certificates/2018/datacamp-introduction-to-r.pdf), Datacamp.

[Lógica de Programação](https://beatrizmilz.github.io/resume/certificates/2018/Soft-blue-Logica-de-Programacao.pdf), Softblue, 20h.




### 2017

N/A

N/A

2017


`GIS` - [Workshop de QGIS – Acessando dados abertos e georreferenciamento](https://beatrizmilz.github.io/resume/certificates/2017/fna_geotecnologia_workshop_dados_abertos.pdf), Estúdio
Registro, 4h.

`GIS` - Geoprocessamento para Planejamento e Gestão Ambiental, SENAC, 32h.

```{r eval=FALSE, include=FALSE}

Retirei do currículo
 Avaliação de Impacto Ambiental nos Sistemas Aquáticos Continentais, XVI
Congresso Brasileiro de Limnologia, 5h.
```


### 2016

N/A

N/A

2016

Expressão Verbal - desinibição ao falar em público, SENAC, 24h.

Legislação Ambiental, SENAC, 40h.


```{r eval=FALSE, include=FALSE}

Retirei do currículo

Elaboração, Avaliação e Gestão de Projetos Socioambientais, Serviço Municipal de Saneamento Ambiental de Santo André (SEMASA), 10h.
```

### 2015

N/A

N/A

2015

Excel 2010 Módulo II, Empresa de Tecnologia da Informação e Comunicação do Município de São Paulo (PRODAM-SP), 20h.

ACCESS 2010 Módulo I, Empresa de Tecnologia da Informação e Comunicação do Município de São Paulo (PRODAM-SP), 20h.

[Mudanças climáticas, recursos hídricos e educação ambiental](https://beatrizmilz.github.io/resume/certificates/2015/oficina_munic_Mudancas_climaticas.jpg), Oficina Municipal – Escola de cidadania e gestão pública, 14h.


### 2014

N/A

N/A

2014

`GIS` - Mapa Digital da Cidade – MDC, Departamento de Produção e Análise de Informação – DEINFO da Secretaria Municipal de Desenvolvimento Urbano – SMDU, 3h.

`GIS` - Uso do SIG-GCM e Capacitação do Aplicativo GEO-SIG-GCM, Guarda Civil Metropolitana/SMSU/PMSP, 8h.

`GIS` - Introdução aos Sistemas de Informação Geográfica – Prática com Quantum GIS, Instituto GEOeduc, 8h.

`GIS` - Introdução ao Processamento Digital de Imagens – Prática com Quantum GIS Instituto GEOeduc, 8h.

Excel 2010 Módulo I, Empresa de Tecnologia da Informação e Comunicação do Município de São Paulo (PRODAM-SP), 20h.



