---
title: ""
format: 
  html:
    theme: journal
    css: custom.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- "https://docs.google.com/spreadsheets/d/1iBxpNzwZWOrOwR__Y4FNDQ_3tpw-0trS0PVigsS4z6w/edit?usp=sharing"
cv <- googlesheets4::read_sheet(cv_url)
```

::: columns
::: {.column width="25%"}
<center><a href='https://beamilz.com' target='_blank'> ![](https://avatars.githubusercontent.com/u/42153618?v=4){width="80%" style="border-radius: 50%;"}</center>

</a>

### Contact

<center><span style="font-size: 1.5em;"> <a href='https://beamilz.com' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/beatrizmilz' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:milz.bea@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://twitter.com/BeaMilz' target='_blank'><i class="fa-brands fa-twitter"></i></a> <a href='https://discourse.curso-r.com/u/beatrizmilz/summary' target='_blank'><i class="fab fa-discourse"></i></a></center>

</span>

Hi! I'm a co-organizer of [R-Ladies São Paulo](https://www.instagram.com/rladiessaopaulo/) since 2018, and I have taught in several meetups and workshops. All the slides are available here: [beamilz.com/talks/](https://beamilz.com/talks/). I'm also a co-organizer of [satRday São Paulo](https://saopaulo2019.satrdays.org/) and [LatinR](https://latin-r.com/).

### Teaching

<i class="fas fa-chalkboard-teacher"></i> [`tidyverse` certified trainer by RStudio](https://education.rstudio.com/trainers/people/milz+beatriz/). <br> <i class="fas fa-chalkboard-teacher"></i> [The Carpentries instructor](https://carpentries.org/).

### Languages

**Portuguese:** Native <br> **English:** Proficient <br> **Spanish:** Proficient

### Grants

<i class="far fa-star"></i> [rstudio::conf() 2022](https://www.rstudio.com/conference/) - Diversity Scholarship.

<i class="far fa-star"></i> [FAPESP](https://fapesp.br/). Doctorate Scholarship - 2019-2021.

<i class="far fa-star"></i> [useR! 2019](https://user2019.r-project.org/) - Diversity Scholarship.

<i class="far fa-star"></i> [LatinR 2019](https://latin-r.com/) - Diversity Scholarship.

### Software review

<i class="fas fa-box-open"></i> [R OpenSci](https://ropensci.org/): [reviews available here](https://github.com/beatrizmilz/ropensci_reviews#ropensci-reviews).

### Software

<i class="fas fa-box-open"></i> [Package {dados} - Available on CRAN](https://cienciadedatos.github.io/dados/) - Co-Author.

<i class="fas fa-box-open"></i> [Package {mananciais}](https://beatrizmilz.github.io/mananciais/) - Author, maintainer.

### Programming skills

<i class="fab fa-r-project"></i> `R` <br> <i class="fa fa-area-chart" aria-hidden="true"></i> `tidyverse` <br> <i class="fab fa-markdown"></i> `RMarkdown / Quarto` <br> <i class="fas fa-code-branch"></i> `Git` <br> <i class="fab fa-github"></i> `GitHub` <br> <i class="fab fa-markdown"></i> `Markdown` <br> <i class="fab fa-html5"></i> `HTML` <br> <i class="fab fa-css3-alt"></i> `CSS` <br>
:::

::: {.column width="5%"}
:::

::: {.column width="70%"}
<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}

col_br_loc <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<br><i class="fa-solid fa-location-dot"></i> ', col),
      ""
    )
}

create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", NA_character_, loc)) |>
    dplyr::filter(in_resume %in% c("TRUE", "VERDADEIRO"), section == section_name) |>
    dplyr::select(section:description_1) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Current <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> {col_br(institution)} {col_br(description_1)} {col_br_loc(loc)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, loc, description_1)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text) |> 
    gt::cols_width(date ~ gt::pct(10))
}
```



<!-- Main content -->

# Beatriz Milz

## <i class="fa-solid fa-suitcase"></i> Work

```{r}
create_section(cv, "working_experience")
```

## <i class="fa-solid fa-person-chalkboard"></i> Selected teaching experience

```{r}
create_section(cv, "teaching_experience")
```

<br> 

## <i class="fa-solid fa-chalkboard-user"></i> Selected talks / workshops

```{r}
create_section(cv, "oral_communications")
```

[See more in beamilz.com/talks/](https://beamilz.com/talks/)

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_section(cv, "education")
```

<p class="small">

Resume made with 💜 and [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available on <i class="fa-brands fa-github"></i> [GitHub](https://github.com/beatrizmilz/resume/blob/master/docs/index.qmd). <br>License: [CC BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/).

</p>

:::
:::



```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
